Online reprocessing simulation for thorium-fueled molten salt breeder reactor

### 2017-08-07 msbr_reproc.tex
Neutron spectrum normalized by lethargy, STD for K-eff added

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=0.95\linewidth]{zone_I_mesh.png}
        \caption{MSBR unit cell of Zone I geometry.}
        \label{fig:zoneI}
\end{figure}

@@

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
a state with fully withdrawn control rods, which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm.Figure~\ref{fig:keff} 
shows the infinite multiplication factor for 1200-days reprocessing cycle calculated by 
Serpent 2 with ENDF/B-VII.0 nuclear data. A 
significant standard deviation (100 pcm) causes the multiplication factor 
fluctuations visible in this plot.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{keff.png}
        \caption{Infinite multiplication factor during a 1200 days depletion
        simulation.}
        \label{fig:keff}
\end{figure}

@@

Protactinium-233 continuously removing into the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
The infinite multiplication factor decreases first 400 days of depletion due to 
strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
reactor operation producing fissile materials other than $^{233}$U in the core 
(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
refill rate after ~1 year of operation.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.03\linewidth]{fuel_composition.png}
        \caption{Normalized number density of major isotopes during 1200 days of 
        depletion.}
        \label{fig:compos}
\end{figure}

@@

Figure~\ref{fig:spectrum} represents the normalized neutron flux distribution 
of the initial and the equilibrium core compositions. The spectrum for the 
equilibrium state is harder than the initial state due to heavy fission 
products.  
\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.04\linewidth]{spectrum.png}
        \caption{Normalized neutron energy spectrum for initial and equilibrium 
        composition.}
        \label{fig:spectrum}
\end{figure}

>>>>

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=0.95\linewidth]{zone_I_mesh.png}
        \caption{MoltenSalt Breeder Reactor (MSBR) unit cell of Zone I geometry.}
        \label{fig:zoneI}
\end{figure}

@@

This analysis models a single representative unit cell rather than the whole 
\gls{MSBR} core. Consequently, it does not take into consideration different 
fuel-moderator volume ratios for Zone I, Zone II, the annulus, and the reflector. The 
initial multiplication factor during depletion calculation is selected for 
a state with fully withdrawn control rods, which gives 
considerable excess reactivity in the beginning of the cycle (approximately 5000 pcm). 
Standard deviation for these calculations is approximately 100 pcm. Figure~\ref{fig:keff} 
shows the infinite multiplication factor for 1200-days reprocessing cycle calculated by 
Serpent 2 with ENDF/B-VII.0 nuclear data. A significant standard deviation causes the 
multiplication factor fluctuations visible in this plot.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.05\linewidth]{keff.png}
        \caption{Infinite multiplication factor during a 1200 days depletion
        simulation.The confidence interval $\pm\sigma$ is shaded.}
        \label{fig:keff}
\end{figure}

@@

Protactinium-233 is continuously removing into the tank for protactinium decay.  $^{233}$Pa has a half-life of 27 days and 
beta decays into $^{233}$U which as fresh fuel goes back to the reactor core. 
The infinite multiplication factor decreases first 400 days of depletion due to 
strong absorbers (e.g. $^{233}$Th, $^{234}$U) accumulation which causes 
relatively high fuel ($^{233}$U) refill inflow to keep reactor critical. During 
reactor operation producing fissile materials other than $^{233}$U in the core 
(e.g. $^{235}$U, $^{239}$Pu) which makes it possible to decrease fresh fuel 
refill rate after ~1 year of operation.

\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.04\linewidth]{fuel_composition.png}
        \caption{Normalized number density of major isotopes during 1200 days of 
        depletion.}
        \label{fig:compos}
\end{figure}

@@

Figure~\ref{fig:spectrum} represents the neutron flux per lethargy energy distribution 
of the initial and the equilibrium core compositions. The spectrum for the 
equilibrium state is harder than the initial state due to heavy fission 
products.  
\begin{figure}[htbp!] % replace 't' with 'b' to force it to be on the bottom
        \centering
        \includegraphics[width=1.05\linewidth]{spectrum.png}
        \caption{Neutron spectrum for initial and equilibrium 
        composition (normalized per lethargy).}
        \label{fig:spectrum}
\end{figure}
